\documentclass[a4paper,10pt]{letter}
\usepackage{lipsum}
\usepackage{hyperref}
\signature{Ahmed Abdelmageed}
\address{Ahmed Abdelmageed \\ ahmad.abdalmageed97@gmail.com \\ +201113510655}
\date{\today}

\begin{document}

\begin{letter}{Kreativstorm Hiring Team}

\opening{Dear Hiring Team,}

I am excited to apply for the Junior Backend Developer position at Kreativstorm, as advertised. With a degree in Computer Science and a strong passion for backend development, I am eager to contribute to your innovative team while further developing my skills in a dynamic and collaborative environment.

During my studies and projects, I have gained proficiency in backend programming languages, particularly Python and Java. I have successfully developed and maintained backend services and APIs, ensuring optimal performance and scalability. My experience working on projects has equipped me with strong problem-solving skills and the ability to troubleshoot server-side issues effectively. I am particularly drawn to this role because of the opportunity to work closely with frontend teams to create seamless integrations that enhance user experiences.

I admire Kreativstorm’s commitment to creativity and continuous improvement. I am eager to collaborate with experienced developers and contribute to impactful projects that drive innovation. I believe my enthusiasm for backend technologies and my dedication to excellence align well with your team’s values.

Thank you for considering my application. I look forward to the opportunity to discuss how my skills and interests can contribute to the success of Kreativstorm.

\closing{Sincerely,}

\end{letter}

\end{document}